Variational Inference for Inverse Reinforcement Learning with Gaussian Processes

### 2019-03-27 mpaper/paper.tex
Some evaluation and a lot of slides

\section{Theoretical Justification} \label{sec:proof}
% TODO: Possible improvements:
% 1. Use limits more often.
% 2. Avoid saying that epsilon is arbitrary and using phrases like 'sufficiently small'.
% TODO: Q should be lowercase

@@

Before that, however, we define a few extra variables in order to simplify
expressions of derivatives:
\begin{align*}
  \mathbf{U} &= (\mathbf{u} - \bm\mu)(\mathbf{u} - \bm\mu)^\intercal, \\
  \mathbf{S} &= \Kru^\intercal\Kuu^{-1}, \\
  \bm\Gamma &= \Krr - \mathbf{S}\Kru, \\
  \mathbf{R} &= \mathbf{S}\frac{\partial \Kru}{\partial \lambda_i} - \frac{\partial \Krr}{\partial \lambda_i} + \left( \frac{\partial \Kru^\intercal}{\partial \lambda_i} - \mathbf{S}\frac{\partial \Kuu}{\partial \lambda_i} \right) \Kuu^{-1}\Kru, \\
  Q &= (\mathbf{u} - \bm\mu)^\intercal\bm\Sigma^{-1}(\mathbf{u} - \bm\mu).
\end{align*}
Also note that throughout this section the word `constant' means `constant with
respect to $\mathbf{u}$ and $\mathbf{r}$'.

@@

\begin{figure*}
  \centering
  \begin{minipage}{.5\textwidth}
    \centering
    \includegraphics[width=0.8\columnwidth]{figures/convergence1}
  \end{minipage}%
  \begin{minipage}{.5\textwidth}
    \centering
    \includegraphics[width=0.8\columnwidth]{figures/convergence2}
  \end{minipage}
  \caption{The convergence of $\mathcal{L}$ (at the top) and several example
    policies (at the bottom) over a number of iterations for Scenario~1 on the
    left and Scenario~2 on the right.}
  \label{fig:convergence1}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{figures/parameter_convergence1}
  \caption{Convergence of all optimised parameters for Scenario~1 at the top and
  Scenario~2 at the bottom. In order to represent different variables on the
  same scale, some variables have been $\log$-transformed. Colours denote which
  vector or matrix each scalar comes from: black for $\bm\lambda$,
  \textcolor{blue}{blue} for $\bm\mu$, \textcolor{red}{red} for diagonal
  elements of $\mathbf{B}$, and \textcolor{green}{green} for its non-diagonal
  elements.}
  \label{fig:convergence2}
\end{figure*}

We plot how $\mathcal{L}$ as well as policies $\pi(a_1 \mid s_1)$, $\pi(a_2 \mid
s_3)$, and $\pi(a_1 \mid s_2)$ converge over a number of iterations in Figure
\ref{fig:convergence1}. The first two policies correspond to actions taken in
the set of demonstrations $\mathcal{D}$, so we would expect to see their
probabilities converge to values near $1$. The third policy, however, has no
data in $\mathcal{D}$ that would guide its value, so the maximum causal entropy
framework would put the probability at around $0.5$.

% TODO: rewrite this
As we ran the algorithm with two stopping conditions---$300$ iterations and the
$\ell_1$-norm of the change in parameter values being below $0.01$---note that
the algorithm terminated early in Scenario~2 but not in Scenario~1, although
there is clear convergence in both cases. An important difference is that
$\pi(a_1 \mid s_1)$ and $\pi(a_2 \mid s_3)$ converge closer and closer to $1$
with the slightly-restricted model of Scenario~1, but stabilise at $0.6$ in
Scenario~2 due to an important part of the model being completely fixed. In both
cases, $\pi(a_1 \mid s_2)$ converges to $0.5$ as expected.

% TODO: rewrite
Figure \ref{fig:convergence2} shows how the parameters of the model converge in
both scenarios. The algorithm seems to converge fine in Scenario~2, but most of
the parameters fail to stabilise in Scenario~1. Most importantly, the diagonal
values of the $\mathbf{B}$ matrix diverge to positive infinity, leading to higher
variance in ELBO estimates seen in Figure \ref{fig:convergence1}. The
non-diagonal values, however, converge just fine. Both $\lambda_0$ and
$\lambda_1$ also diverge to positive infinity, while the elements of $\bm\mu$
diverge, but in `the right' direction: as $\mu_2$ increases while $\mu_1$ and
$\mu_3$ decrease, the policies in Figure \ref{fig:convergence1} converge to
their optimal values.

\begin{figure}
  \centering
  \begin{tikzpicture}[
    /pgfplots/colormap/violet,
    ellipse2/.style={
      draw,
      ellipse,
      /utils/exec={
        \pgfplotscolormapdefinemappedcolor{#1}},
      fill=mapped color},
    edge2/.style={
      ultra thick,
      /utils/exec={
        \pgfplotscolormapdefinemappedcolor{#1}},
      draw=mapped color}]
    \csvreader[
    no head,
    column count=11
    ]{data/median_covariance_transformed.csv}{1=\x, 2=\y, 3=\Soneone, 4=\Stwotwo, 5=\Sthreethree, 6=\Stwoone, 7=\Sthreeone, 8=\Sthreetwo}{%
      \node[ellipse2=\Soneone] (s1) at (3*\x, 2*\y) {$s_1$};
      \node[ellipse2=\Stwotwo] (s2) at (3*\x+1, 2*\y+1) {$s_2$};
      \node[ellipse2=\Sthreethree] (s3) at (3*\x+2, 2*\y) {$s_3$};
      \draw[edge2=\Stwoone] (s1) -- (s2);
      \draw[edge2=\Sthreeone] (s1) to (s3);
      \draw[edge2=\Sthreetwo] (s2) to (s3);
    }
    \draw [<->] (2.5, 7.5) node (yaxis) [above] {$\zeta_2$}
    |- (11.5, 1.5) node (xaxis) [right] {$\zeta_1$};
    \foreach \x in {1, 2, 3} {
      \node (x\x) at (1+3*\x, 1.3) {$\x$};
    }
    \foreach \y in {1, 2, 3} {
      \node (y\y) at (2.3, 0.5+2*\y) {$\y$};
    }
  \end{tikzpicture}
  \end{figure}

\begin{figure}
  \centering
  \begin{tikzpicture}
    \csvreader[
    no head,
    column count=11
    ]{data/covariance_and_policy_transformed.csv}{1=\x, 2=\y, 3=\Soneone, 4=\Stwotwo, 5=\Sthreethree, 6=\Stwoone, 7=\Sthreeone, 8=\Sthreetwo, 9=\ponetwo, 10=\ptwoone, 11=\pthreetwo}{%
      \begin{axis}[
        ybar=0,
        symbolic x coords={a,b,c},
        ticks=none,
        ymax=1,
        ymin=0,
        x=20,
        bar width=20,
        enlarge x limits=0.25,
        at={(350*\x, 110*\y)},
        height=100,
        bar shift=0pt,
        legend style={
          legend columns=-1,
          at={(1.7,-0.4)}
        }
        ]
        \addplot coordinates {(a, \ponetwo)};
        \addplot coordinates {(b, \ptwoone)};
        \addplot coordinates {(c, \pthreetwo)};
        \draw[dashed] (-50,50) -- (270,50);
        \ifthenelse{\x=2 \AND \y=1}{
          \legend{$\pione$,$\pitwo$,$\pithree$};
        }{}
      \end{axis}
    }
    \draw [<->] (2.3, 8.5) node (yaxis) [above] {$\zeta_2$}
    |- (10, 2) node (xaxis) [right] {$\zeta_1$};
    \foreach \x in {1, 2, 3} {
      \node (x\x) at (1+2.5*\x, 1.7) {$\x$};
    }
    \foreach \y in {1, 2, 3} {
      \node (y\y) at (2.1, 1+2.1*\y) {$\y$};
    }
  \end{tikzpicture}
  \caption{How policy probabilities change after adding more demonstrations. The
    $x$-axis ($y$-axis) shows how many copies of $\zeta_1$ ($\zeta_2$) were in
    $\mathcal{D}$. Each plot shows the values of three policies after 300
    iterations (averaged out over 10 runs). The bottom (top) of each bar plot
    corresponds to probability 0 (1), and dashed lines mark probability 0.5.}
  \label{fig:policies}
\end{figure}

We would expect stochastic probabilities to converge closer to extreme
values (i.e., 0 and 1) as we add more data to the model. We test this hypothesis
with a small-scale experiment in Figure \ref{fig:policies}. The policy $\pitwo$,
in particular, confirms our prediction. As this policy denotes the probability
of going from $s_2$ to $s_1$, we expect it to stay around $0.5$ as long as we
have equal amounts of demonstrations $\zeta_1$ and $\zeta_2$ (this corresponds
to the plots at coordinates $(1, 1)$, $(2, 2)$, and $(3, 3)$). But as we
increase the number of times state $s_1$ appears in our demonstrations (going
to the right across any row of plots), the model recognises the increasing value
of state $s_1$, and the probability increases. In contrast, going up across the
plots reduces the probability, as state $s_3$ becomes more valuable, and the
model prefers it over state $s_1$. Interestingly, the other two policy
probabilities seem to increase with any added data. This is likely due to the
fact that more demonstrations result in higher gradient values, and thus lead to
better-converged policies.

%The experiments were run with a constant step size of 0.1, discarding iterations where either $\bm\Sigma$ or $\bm\Gamma$ becomes near-singular.

%Diagonal and non-diagonal entries of the covariance matrix are normalised to
%$[0, 1]$ separately, so as to emphasize the variation in each. There were no
%negative entries of the covariance matrix after convergence.

%More data creates bigger gradients---need smaller step size. Dynamic step sizes
%don't work very well because they become zero after a big spike (and spikes do
%happen).
\section{Related Work} % 0.5-1 page

@@

\begin{itemize}
\item Why my theoretical contributions are important...
\item Reasonable results with convergence: policies do converge to optimal
  values, even at the extremes (i.e., $0$ and $1$).
\item Shown how to eliminate the deterministic training conditional
  assumption---a common weakness of previous approaches.
\item Being able to model rewards using full probability distributions without
  limiting assumptions opens up many new research directions.
\end{itemize}

@@

\derivatives*
\begin{proof}
  \leavevmode
  \begin{enumerate}
  \item
    \[
      \begin{split}
        \frac{\partial q(\mathbf{u})}{\partial m} &=
        q(\mathbf{u})\dm\left[-\frac{Q}{2}\right]
        \\
        &= -\frac{1}{2}q(\mathbf{u})(\bm\Sigma^{-1} +
        \bm\Sigma^{-\intercal})(\mathbf{u} - \bm\mu)\dm[\mathbf{u} -
        \bm\mu] \\
        &= \frac{1}{2}q(\mathbf{u})(\bm\Sigma^{-1} +
        \bm\Sigma^{-\intercal})(\mathbf{u} - \bm\mu).
      \end{split}
    \]
  \item An online tool by Laue et
    al.\footnote{\url{http://www.matrixcalculus.org/}}
    \cite{DBLP:conf/nips/LaueMG18} can be used to find both derivatives.
  \item
    \begin{enumerate}
    \item Since
    \begin{align*}
      q(\mathbf{r} \mid \mathbf{u}) &= \mathcal{N}(\mathbf{r};
      \Kru^\intercal\Kuu^{-1}\mathbf{u}, \Krr - \Kru^\intercal \Kuu^{-1}\Kru) \\
      &= \mathcal{N}(\mathbf{r}; \mathbf{Su}, \bm\Gamma),
    \end{align*}
    we have
    \[
      \frac{\partial q(\mathbf{r} \mid \mathbf{u})}{\partial \lambda_i} =
      -\frac{1}{2}q(\mathbf{r} \mid \mathbf{u}) \dl[(\mathbf{r} -
      \mathbf{Su})^\intercal\bm\Gamma^{-1}(\mathbf{r} - \mathbf{Su}) +
      \log|\bm\Gamma|].
    \]
    The same online tool can be used to show that
    \[
      \dl \log|\bm\Gamma| = -|\bm\Gamma|^{-1}\tr(\mathbf{R}\adj(\bm\Gamma)),
    \]
    and
    \[
      \dl \bm\Gamma^{-1} = \bm\Gamma^{-1}\mathbf{R}\bm\Gamma^{-1}.
    \]
  \item
    If $i=0$, then
    \[
      \frac{\partial \mathbf{K}}{\partial \lambda_i} =
      \frac{1}{\lambda_i}\mathbf{K}
    \]
    by the structure of each element of $\mathbf{K}$. If $i \ne 0$, then each
    element of $\frac{\partial \mathbf{K}}{\partial \lambda_i}$ is
    \begin{align*}
      L_{j,k} &= \frac{\partial k(\mathbf{x}_j, \mathbf{x}_k)}{\partial \lambda_i} \\
      &\begin{aligned}
        = k(\mathbf{x}_j, \mathbf{x}_k) \dl \left[ \vphantom{\frac{1}{2}} \right. &-\frac{1}{2}(\mathbf{x}_j - \mathbf{x}_k)^\intercal \bm\Lambda (\mathbf{x}_j - \mathbf{x}_k) \\
        &- \mathbbm{1}[j \ne k]\sigma^2\tr(\bm\Lambda) \left. \vphantom{\frac{1}{2}} \right]
      \end{aligned} \\
      &\begin{aligned}
        = k(\mathbf{x}_j, \mathbf{x}_k) \dl \left[ \vphantom{\sum_{k=1}^d} \right. &-\frac{1}{2} \sum_{l=1}^d \lambda_l (x_{j,l} - x_{k,l})^2 \\
        &- \mathbbm{1}[j \ne k]\sigma^2\sum_{l=1}^d \lambda_l \left. \vphantom{\sum_{l=1}^d} \right]
      \end{aligned} \\
      &= k(\mathbf{x}_j, \mathbf{x}_k) \left( -\frac{1}{2}(x_{j,i} - x_{k,i})^2 - \mathbbm{1}[j \ne k]\sigma^2 \right).
    \end{align*}
    \end{enumerate}
  \end{enumerate}
\end{proof}

>>>>

\section{Theoretical Justification} \label{sec:proof}
% TODO: Possible improvements:
% 1. Use limits more often.
% 2. Avoid saying that epsilon is arbitrary and using phrases like 'sufficiently small'.

@@

Before that, however, we define a few extra variables in order to simplify
expressions of derivatives:
\begin{align*}
  \mathbf{U} &= (\mathbf{u} - \bm\mu)(\mathbf{u} - \bm\mu)^\intercal, \\
  \mathbf{S} &= \Kru^\intercal\Kuu^{-1}, \\
  \bm\Gamma &= \Krr - \mathbf{S}\Kru, \\
  \mathbf{R} &= \mathbf{S}\frac{\partial \Kru}{\partial \lambda_i} - \frac{\partial \Krr}{\partial \lambda_i} + \left( \frac{\partial \Kru^\intercal}{\partial \lambda_i} - \mathbf{S}\frac{\partial \Kuu}{\partial \lambda_i} \right) \Kuu^{-1}\Kru.
\end{align*}
Also note that throughout this section the word `constant' means `constant with
respect to $\mathbf{u}$ and $\mathbf{r}$'.

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{figures/convergence_new}
  \caption{Convergence of $\mathcal{L}$ (at the top) as well as several example
    policies (at the bottom).}
  \label{fig:convergence1}
\end{figure}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{figures/parameter_convergence_new}
  \caption{Convergence of variational parameters. In order to represent
    different variables on the same scale, some variables have been
    $\log$-transformed. Colours denote which vector or matrix each scalar comes
    from: black for $\bm\lambda$, \textcolor{blue}{blue} for $\bm\mu$,
    \textcolor{red}{red} for diagonal elements of $\mathbf{B}$, and
    \textcolor{green}{green} for its non-diagonal elements.}
  \label{fig:convergence2}
\end{figure*}

We plot how $\mathcal{L}$ as well as policies $\pi(a_1 \mid s_1)$, $\pi(a_2 \mid
s_3)$, and $\pi(a_1 \mid s_2)$ converge over a number of iterations in Figure
\ref{fig:convergence1}. The first two policies correspond to actions taken in
the set of demonstrations $\mathcal{D}$, so we would expect to see their
probabilities converge to values near $1$. The third policy, however, has no
data in $\mathcal{D}$ to guide its value, so the maximum causal entropy
framework would put the probability at around $0.5$. The first thing to note is
that while $\mathcal{L}$ converges in just a few iterations, policies continue
to improve for much longer. In addition, all policies behave as expected:
$\pitwo$ stays around $0.5$, while both $\pione$ and $\pithree$ keep increasing.
Although they stay at around $0.75$ (and not 1), this may be optimal for the
maximum causal entropy model (and this question will be addressed in more detail
with a different experiment).

We also plot how the parameters of the model converge in Figure
\ref{fig:convergence2}. While some parameters could benefit from a higher number of
iterations\footnote{The limit of 300 iterations was chosen so that the initial
  increase in $\mathcal{L}$ would not be overshadowed by a long straight line
  afterwards.}, none look alarmingly wrong. Note that $\mu_2$, a variable
closely related to $r(s_2)$, stabilises at a positive value whereas both $\mu_1$
and $\mu_2$ become negative.

\begin{figure}
  \centering
  \begin{tikzpicture}
    \csvreader[
    no head,
    column count=11
    ]{data/covariance_and_policy_transformed.csv}{1=\x, 2=\y, 3=\Soneone, 4=\Stwotwo, 5=\Sthreethree, 6=\Stwoone, 7=\Sthreeone, 8=\Sthreetwo, 9=\ponetwo, 10=\ptwoone, 11=\pthreetwo}{%
      \begin{axis}[
        ybar=0,
        symbolic x coords={a,b,c},
        ticks=none,
        ymax=1,
        ymin=0,
        x=20,
        bar width=20,
        enlarge x limits=0.25,
        at={(350*\x, 110*\y)},
        height=100,
        bar shift=0pt,
        legend style={
          legend columns=-1,
          at={(1.7,-0.4)}
        }
        ]
        \addplot coordinates {(a, \ponetwo)};
        \addplot coordinates {(b, \ptwoone)};
        \addplot coordinates {(c, \pthreetwo)};
        \draw[dashed] (-50,50) -- (270,50);
        \ifthenelse{\x=2 \AND \y=1}{
          \legend{$\pione$,$\pitwo$,$\pithree$};
        }{}
      \end{axis}
    }
    \draw [<->] (2.3, 8.5) node (yaxis) [above] {$\zeta_2$}
    |- (10, 2) node (xaxis) [right] {$\zeta_1$};
    \foreach \x in {1, 2, 3} {
      \node (x\x) at (1+2.5*\x, 1.7) {$\x$};
    }
    \foreach \y in {1, 2, 3} {
      \node (y\y) at (2.1, 1+2.1*\y) {$\y$};
    }
  \end{tikzpicture}
  \caption{Changes in policies after adding more demonstrations. The $x$-axis
    ($y$-axis) shows how many copies of $\zeta_1$ ($\zeta_2$) are in
    $\mathcal{D}$. Each plot shows the values of three policies after 300
    iterations (averaged out over 10 runs). The bottom (top) of each bar plot
    corresponds to probability 0 (1), and dashed lines mark probability
    0.5.}
  \label{fig:policies}
\end{figure}

We would expect policies to converge closer to extreme values (i.e., 0 and 1) as
we add more data to the model. We test this hypothesis with a small-scale
experiment in Figure \ref{fig:policies}. The policy $\pitwo$, in particular,
confirms our prediction. As this policy denotes the probability of going from
$s_2$ to $s_1$, we expect it to stay around $0.5$ as long as we have equal
amounts of $\zeta_1$ and $\zeta_2$ (this corresponds to the plots at coordinates
$(1, 1)$, $(2, 2)$, and $(3, 3)$). But as we increase the number of times state
$s_1$ appears in our demonstrations (going to the right across any row of
plots), the model recognises the increasing value of state $s_1$, and the
probability increases. In contrast, going up across the plots reduces the
probability, as state $s_3$ becomes more valuable, and the model prefers it over
state $s_1$. Interestingly, the other two policy probabilities seem to increase
regardless of what data is added. This is likely due to the fact that a higher
number of demonstrations results in higher gradient values, and thus leads to
better-converged policies.

\begin{figure}[!ht]
  \centering
  \begin{tikzpicture}[
    /pgfplots/colormap/violet,
    ellipse2/.style={
      draw,
      ellipse,
      /utils/exec={
        \pgfplotscolormapdefinemappedcolor{#1}},
      fill=mapped color},
    edge2/.style={
      ultra thick,
      /utils/exec={
        \pgfplotscolormapdefinemappedcolor{#1}},
      draw=mapped color}]
    \csvreader[
    no head,
    column count=11
    ]{data/median_covariance_transformed.csv}{1=\x, 2=\y, 3=\Soneone, 4=\Stwotwo, 5=\Sthreethree, 6=\Stwoone, 7=\Sthreeone, 8=\Sthreetwo}{%
      \node[ellipse2=\Soneone] (s1) at (2*\x, 2*\y) {$s_1$};
      \node[ellipse2=\Stwotwo] (s2) at (2*\x+0.5, 2*\y+1) {$s_2$};
      \node[ellipse2=\Sthreethree] (s3) at (2*\x+1, 2*\y) {$s_3$};
      \draw[edge2=\Stwoone] (s1) -- (s2);
      \draw[edge2=\Sthreeone] (s1) to (s3);
      \draw[edge2=\Sthreetwo] (s2) to (s3);
    }
    \draw [<->] (1.5, 7.5) node (yaxis) [above] {$\zeta_2$}
    |- (8, 1.5) node (xaxis) [right] {$\zeta_1$};
    \foreach \x in {1, 2, 3} {
      \node (x\x) at (0.5+2*\x, 1.3) {$\x$};
    }
    \foreach \y in {1, 2, 3} {
      \node (y\y) at (1.3, 0.5+2*\y) {$\y$};
    }
    \begin{axis}[
      colormap/violet,
      scale only axis,
      width=0pt,
      height=0pt,
      hide axis,
      colorbar horizontal,
      point meta min=-1,
      point meta max=1,
      xshift=40,
      yshift=30,
      colorbar style={
        width=6.5cm,
        xtick={-1,0,1},
        xlabel=normalised covariance,
      }]
      \addplot [draw=none] coordinates {(0,0)};
    \end{axis}
  \end{tikzpicture}
  \caption{Changes in reward covariances after adding more demonstrations. The
    meaning of external axes is the same as in Figure \ref{fig:policies}.
    Colours denote reward covariance values, e.g., the colour of node $s_1$
    denotes the variance of $r(s_1)$, and the colour of the edge between nodes
    $s_1$ and $s_2$ denotes the covariance between $r(s_1)$ and $r(s_2)$. The
    colours represent median covariances across 10 runs, normalised to the
    interval $[-1, 1]$ while preserving their positivity/negativity.}
  \label{fig:covariance}
\end{figure}

Finally, we would like to see similar changes in reward covariances. Firstly, we
will show how to derive the covariance matrix for $\mathbf{r}$ from the
posterior distributions of $\mathbf{u}$ and $\mathbf{r} \mid \mathbf{u}$.
Remember that $\mathbf{u} \sim \mathcal{N}(\bm\mu, \bm\Sigma)$ and $\mathbf{r}
\mid \mathbf{u} \sim \mathcal{N}(\mathbf{Su}, \bm\Gamma)$, and let $\mathbf{r}
\sim \mathcal{N}(\bm\mu', \bm\Sigma')$, where our goal is to find $\bm\mu'$ and
$\bm\Sigma'$. Then
\[
  \bm\mu' = \mathbb{E}[\mathbf{r}] = \mathbb{E}[\mathbf{Su}] = \mathbf{S}\bm\mu.
\]
Furthermore,
\begin{align*}
  \mathbb{E}_{\mathbf{r}}[\mathbf{rr}^\intercal] &= \bm\Gamma + \mathbb{E}_{\mathbf{u}}[\mathbf{Suu}^\intercal\mathbf{S}^\intercal] = \bm\Gamma + \mathbf{S}\mathbb{E}_{\mathbf{u}}[\mathbf{uu}^\intercal]\mathbf{S}^\intercal \\
                                                 &= \bm\Gamma + \mathbf{S}(\bm\Sigma + \bm\mu\bm\mu^\intercal)\mathbf{S}^\intercal
\end{align*}
by the identity for $\mathbb{E}[\mathbf{xx}^\intercal]$ from the book by
Petersen and Pedersen \cite{petersen2008matrix}. Now we can find the covariance
matrix as follows:
\begin{align*}
  \bm\Sigma' &= \mathbb{E}[(\mathbf{r} - \mathbf{S}\bm\mu)(\mathbf{r} -
               \mathbf{S}\bm\mu)^\intercal] \\
             &= \mathbb{E}[\mathbf{rr}^\intercal - \mathbf{r}\bm\mu^\intercal\mathbf{S}^\intercal - \mathbf{S}\bm\mu\mathbf{r}^\intercal + \mathbf{S}\bm\mu\bm\mu^\intercal\mathbf{S}^\intercal] \\
             &= \bm\Gamma + \mathbf{S}\bm\Sigma\mathbf{S}^\intercal.
\end{align*}
Therefore, $\mathbf{r} \sim \mathcal{N}(\mathbf{S}\bm\mu, \bm\Gamma +
\mathbf{S}\bm\Sigma\mathbf{S}^\intercal)$.

Secondly, we normalise the elements of this new covariance matrix into the
interval $[-1, 1]$ for visualisation purposes. Diagonal (state) and non-diagonal
(edge) covariances are normalised separately in order to represent the full
range of values more clearly. All covariances are normalised according to this
rule:
\[
  x \mapsto
  \begin{cases*}
    x/M & if $x \ge 0$ \\
    -x/m & otherwise,
  \end{cases*}
\]
where $M$ is the maximum (diagonal or non-diagonal) covariance across all data,
and $m$ is the minimum. This way, all covariances are scaled to $[-1, 1]$, with
both extreme points guaranteed to be reached unless all values are on one side
of zero on the real number axis.

Unfortunately, the resulting plot in Figure \ref{fig:covariance} shows no clear
pattern. The only worthwhile observation is that there are only two instances of
negative covariance, and both of them are between states $s_2$ and $s_3$.
Perhaps there is a good (currently unknown) reason for why adding more data does
not reduce variance, or perhaps this plot could benefit from a higher number of
iterations and more repeated experiments to ensure the accuracy of the results.
% or a different MDP, like a star

% EXTRA INFO:
% Discarding iterations where either $\bm\Sigma$ or $\bm\Gamma$ becomes near-singular.
%Diagonal and non-diagonal entries of the covariance matrix are normalised to
%$[0, 1]$ separately, so as to emphasize the variation in each. There were no
%negative entries of the covariance matrix after convergence.
%More data creates bigger gradients---need smaller step size. Dynamic step sizes
%don't work very well because they become zero after a big spike (and spikes do
%happen).
\section{Related Work} % 0.5-1 page

@@

\begin{itemize}
\item Why my theoretical contributions are important...
\item Reasonable results with policy convergence.
\item Shown how to eliminate the deterministic training conditional
  assumption---a common weakness of previous approaches.
\item Being able to model rewards using full probability distributions without
  limiting assumptions opens up many new research directions.
\item Determining how reward covariance depends on data would be the next step.
\end{itemize}

@@

\derivatives*
\begin{proof}
  \leavevmode
  \begin{enumerate}
  \item
    \begin{align*}
      \frac{\partial q(\mathbf{u})}{\partial m} &= q(\mathbf{u})\dm\left[-\frac{(\mathbf{u} - \bm\mu)^\intercal\bm\Sigma^{-1}(\mathbf{u} - \bm\mu)}{2}\right] \\
                                                &= -\frac{1}{2}q(\mathbf{u})(\bm\Sigma^{-1} + \bm\Sigma^{-\intercal})(\mathbf{u} - \bm\mu)\dm[\mathbf{u} - \bm\mu] \\
                                                &= \frac{1}{2}q(\mathbf{u})(\bm\Sigma^{-1} + \bm\Sigma^{-\intercal})(\mathbf{u} - \bm\mu).
    \end{align*}
  \item An online tool by Laue et
    al.\footnote{\url{http://www.matrixcalculus.org/}}
    \cite{DBLP:conf/nips/LaueMG18} can be used to find both derivatives.
  \item
    \begin{enumerate}
    \item Since
    \begin{align*}
      q(\mathbf{r} \mid \mathbf{u}) &= \mathcal{N}(\mathbf{r};
      \Kru^\intercal\Kuu^{-1}\mathbf{u}, \Krr - \Kru^\intercal \Kuu^{-1}\Kru) \\
      &= \mathcal{N}(\mathbf{r}; \mathbf{Su}, \bm\Gamma),
    \end{align*}
    we have
    \[
      \frac{\partial q(\mathbf{r} \mid \mathbf{u})}{\partial \lambda_i} =
      -\frac{1}{2}q(\mathbf{r} \mid \mathbf{u}) \dl[(\mathbf{r} -
      \mathbf{Su})^\intercal\bm\Gamma^{-1}(\mathbf{r} - \mathbf{Su}) +
      \log|\bm\Gamma|].
    \]
    The same online tool can be used to show that
    \[
      \dl \log|\bm\Gamma| = -|\bm\Gamma|^{-1}\tr(\mathbf{R}\adj(\bm\Gamma)),
    \]
    and
    \[
      \dl \bm\Gamma^{-1} = \bm\Gamma^{-1}\mathbf{R}\bm\Gamma^{-1}.
    \]
  \item
    If $i=0$, then
    \[
      \frac{\partial \mathbf{K}}{\partial \lambda_i} =
      \frac{1}{\lambda_i}\mathbf{K}
    \]
    by the structure of each element of $\mathbf{K}$. If $i \ne 0$, then each
    element of $\frac{\partial \mathbf{K}}{\partial \lambda_i}$ is
    \begin{align*}
      L_{j,k} &= \frac{\partial k(\mathbf{x}_j, \mathbf{x}_k)}{\partial \lambda_i} \\
      &\begin{aligned}
        = k(\mathbf{x}_j, \mathbf{x}_k) \dl \left[ \vphantom{\frac{1}{2}} \right. &-\frac{1}{2}(\mathbf{x}_j - \mathbf{x}_k)^\intercal \bm\Lambda (\mathbf{x}_j - \mathbf{x}_k) \\
        &- \mathbbm{1}[j \ne k]\sigma^2\tr(\bm\Lambda) \left. \vphantom{\frac{1}{2}} \right]
      \end{aligned} \\
      &\begin{aligned}
        = k(\mathbf{x}_j, \mathbf{x}_k) \dl \left[ \vphantom{\sum_{k=1}^d} \right. &-\frac{1}{2} \sum_{l=1}^d \lambda_l (x_{j,l} - x_{k,l})^2 \\
        &- \mathbbm{1}[j \ne k]\sigma^2\sum_{l=1}^d \lambda_l \left. \vphantom{\sum_{l=1}^d} \right]
      \end{aligned} \\
      &= k(\mathbf{x}_j, \mathbf{x}_k) \left( -\frac{1}{2}(x_{j,i} - x_{k,i})^2 - \mathbbm{1}[j \ne k]\sigma^2 \right).
    \end{align*}
    \end{enumerate}
  \end{enumerate}
\end{proof}
